True versus apparent shapes of astrophysical bow shocks

### 2016-02-04 papers/Paper1/sec-application.tex
advance on section writing

We measured the Characteristic radii in Orion Nebula proplyds from observations in [OIII] from the Hubble Space Telescope (HST).

>>>>

We measured the Characteristic radii in Orion Nebula proplyds from observations with the ACS camera from the Hubble Space Telescope (HST) using a lamp filter around $\lambda = 5007 \AA$. The observations
